---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# iSEEhex

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/iSEE/iSEEhex)](https://github.com/iSEE/iSEEhex/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/iSEE/iSEEhex)](https://github.com/iSEE/iSEEhex/pulls)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check-bioc](https://github.com/iSEE/iSEEhex/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/iSEE/iSEEhex/actions)
[![Codecov test coverage](https://codecov.io/gh/iSEE/iSEEhex/branch/main/graph/badge.svg)](https://app.codecov.io/gh/iSEE/iSEEhex?branch=main)
<!-- badges: end -->

The goal of `iSEEhex` is to provide panels summarising data points in hexagonal
bins for `r BiocStyle::Biocpkg("iSEE")`.

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install `iSEEhex` from [Bioconductor](http://bioconductor.org/) using the following code:

```{r 'install', eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("iSEEhex")
```

And the development version from [GitHub](https://github.com/iSEE/iSEEhex) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("iSEE/iSEEhex")
```

## Example

For demonstration, we prepare an example `r BiocStyle::Biocpkg("SingleCellExperiment")` object.

```{r example, eval = requireNamespace('iSEEhex'), message=FALSE}
library(scRNAseq)

# Example data ----
sce <- ReprocessedAllenData(assays="tophat_counts")
class(sce)

library(scater)
sce <- logNormCounts(sce, exprs_values="tophat_counts")

sce <- runPCA(sce, ncomponents=4)
sce <- runTSNE(sce)
rowData(sce)$ave_count <- rowMeans(assay(sce, "tophat_counts"))
rowData(sce)$n_cells <- rowSums(assay(sce, "tophat_counts") > 0)
sce
```

Then, we create an `r BiocStyle::Biocpkg("iSEE")` app that compares the
`ReducedDimensionHexPlot` panel -- defined in this package -- to the
standard `ReducedDimensionPlot` defined in the `r BiocStyle::Biocpkg("iSEE")`
package.

```{r}
library(iSEEhex)
initialPanels <- list(
    ReducedDimensionPlot(
        ColorBy = "Feature name", ColorByFeatureName = "Cux2", PanelWidth = 6L),
    ReducedDimensionHexPlot(
        ColorBy = "Feature name", ColorByFeatureName = "Cux2", PanelWidth = 6L,
        BinResolution = 30)
)
app <- iSEE(se = sce, initial = initialPanels)
```

## Citation

Below is the citation output from using `citation('iSEEhex')` in R. Please
run this yourself to check for any updates on how to cite __iSEEhex__.

```{r 'citation', eval = requireNamespace('iSEEhex')}
print(citation('iSEEhex'), bibtex = TRUE)
```

Please note that the `iSEEhex` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `iSEEhex` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The [documentation website](http://iSEE.github.io/iSEEhex) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.

## Code of Conduct

Please note that the iSEEhex project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
