---
title: The iSEEhex package
author:
- name: Kevin Rue-Albrecht
  affiliation: 
  - &id1 MRC Weatherall Institute of Molecular Medicine, University of Oxford,
    Headington, Oxford OX3 9DS, UK.
  email: kevin.rue-albrecht@imm.ox.ac.uk
- name: Federico Marini
  affiliation: 
  - &id2 Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), Mainz
  - Center for Thrombosis and Hemostasis (CTH), Mainz
  email: marinif@uni-mainz.de
- name: Charlotte Soneson
  affiliation: 
  - &id3 Friedrich Miescher Institute for Biomedical Research, Basel
  - SIB Swiss Institute of Bioinformatics
  email: charlottesoneson@gmail.com
- name: Aaron Lun
  email: infinite.monkeys.with.keyboards@gmail.com  
date: "`r BiocStyle::doc_date()`"
package: iSEEhex
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Panel universe}
  %\VignetteEncoding{UTF-8}  
  %\VignettePackage{iSEEhex}
  %\VignetteKeywords{GeneExpression, RNASeq, Sequencing, Visualization, QualityControl, GUI}
  %\VignetteEngine{knitr::rmarkdown}
bibliography: iSEEhex.bib  
---

```{r, echo=FALSE}
knitr::opts_chunk$set(error=FALSE, warning=FALSE, message=FALSE)
library(BiocStyle)
```

```{r, eval=!exists("SCREENSHOT"), include=FALSE}
SCREENSHOT <- function(x, ...) knitr::include_graphics(x)
```

# Overview

The `r Biocpkg("iSEE")` package [@iSEE-2018] provides a general and flexible framework for interactively exploring `SummarizedExperiment` objects.
However, in many cases, more specialized panels are required for effective visualization of specific data types.
The `r Biocpkg("iSEEhex")` package implements a collection of such dedicated panel classes that work directly in the `iSEE` application and can smoothly interact with other panels.
This allows users to quickly parametrize bespoke apps for their data to address scientific questions of interest.
We first load in the package:

```{r}
library(iSEEhex)
```

All the panels described in this document can be deployed by simply passing them into the `iSEE()` function via the `initial=` argument, as shown in the following examples.

#### Where can I find a comprehensive introduction to `r Biocpkg("iSEE")`? {-}

The `r Biocpkg("iSEE")` package contains several vignettes detailing the main functionality. 
You can also take a look at this [workshop](https://iSEE.github.io/iSEEWorkshop2019/index.html). 
A compiled version from the Bioc2019 conference (based on Bioconductor release 3.10) is available [here](http://biocworkshops2019.bioconductor.org.s3-website-us-east-1.amazonaws.com/page/iSEEWorkshop2019__iSEE-lab/).

# Session information {-}

```{r}
sessionInfo()
```

# References {-}
